Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Made the example non-italic.
Ruthless editing

\begin{example}
Take a pattern graph $P$ with vertices $V=\{p, a, b, c, d\}$ and edges $E=\{(a,d), (a,p), (b,c),
(b,d), (b,p), (c,d), (c,p)\}$, which is shown in \cref{fig:klessexample} along with two target
graphs $T_{1}$ and $T_{2}$. The degree of the vertex $p$ in $P$ is $\deg(p)=3$, the neighbours of
$p$ are $\N(p)=\{a,b,c\}$, the neighbourhood degree sequence of $p$ is $\nds(p)=(3,3,2)$, as the
degrees of the neighbours of $p$ are $\deg(a)=2,\ \deg(b)=3$ and $deg(c)=3$.

We can find a subgraph in $T_{1}$ which is non-induced isomorphic to $P$ (indicated through the bold edges and black vertices in $T_{1}$). The vertex $p$ can be  mapped to $t_{1}$ in the target graph $T_{1}$, where $\deg(t_{1})=5$ and $\nds(t_{1})=(5,5,4,2,2)$.

There is a non-induced mapping of the pattern graph $P$ into $T_{2}$ by removing one vertex of $P$. This removal changes the neighbourhood degree sequence of $p$ in the $k$-less version of $P$, to $\nds(p)=(2,2)$.

>>>>

\begin{example}
Consider the pattern graph $P$ and the two target graphs $T_1$ and $T_2$ shown in
\cref{fig:klessexample}. The neighbourhood degree sequence of pattern vertex $p$ is
$\nds(p)=(3,3,2)$.

We highlight a subgraph in $T_{1}$ which is non-induced isomorphic to $P$. The vertex $p$ can be
mapped to $t_{1}$ in the target graph $T_{1}$, as $\nds(t_{1})=(5,5,4,2,2)$.  There is a non-induced
mapping of the pattern graph $P$ into $T_{2}$ by removing the central vertex of $P$.  This removal
changes the neighbourhood degree sequence of $p$ in the $k$-less version of $P$ to $\nds(p)=(2,2)$.
